### 2025-05-20 pre_print/response_to_reviewers.qmd

This is certain to be the case that there will be differential effects over time for the effects of supervision, as would be the case for any training manipulations. As noted inn the discussion already, we are in the process of developing longitudinal research to examine this specifically though. In fact we are in the process currently of developing the protocols and analysis plans for an interrupted time-series with control design with internal replication in order to examine the effects in our members who have changed contracts over time i.e., went from Core to Assisted and vice versa. It is however a complex design and analysis and so, given the already complex approach taken here, we have kept this as a separate piece of follow on work to build further on this area.

### Reviewer Comment

If participants were not blinded to their TUL, is it possible that increased TUL influenced their reported RPE and RPD? Could it influence the outcomes considering the cross-over design?

### Author Response

This certainly could be a confounder for RPE/RPD responses, however this could be a confounder irrespective of whether participants knew their exact TUL or not assuming they have a reasonable perception of time i.e., they could tell if they went longer/shorter than a previous experience they could anchor against and the respond with RPE/RPD as either higher/lower correspondingly. But the randomised cross-over design for the experimental study at least allows for any effect of this to be removed.

### Reviewer Comment

The lack of significant differences in TUL in the retrospective analysis contrasts with findings from the experimental condition. The authors suggest this may be due to more appropriate load prescription in the Assisted group; however, this interpretation is not supported by the retrospective RPE data. If Assisted participants truly trained with a higher (and more optimal) load, one would expect their RPE scores to be notably higher, yet this was not observed.

### Author Response

This interpretation is more speculative and in reference to the Core vs Assisted contrast in the previous observational sample only. However, the Core vs Assisted RPE contrasts are actually of similar magnitudes in both the previous observational sample and the experimental data. So whilst the absolute magnitudes are still low for the previous sample, the difference between conditions is still similar to that seen in the experimental data. So, it is perhaps plausible that more appropriate loads during Assisted compared to Core may be a reason for this even if they are still suboptimal. But we do also somewhat test this explanation and note the exploratory examination of some of our load progression data which suggests that load progressions may be similar in the footnote. As noted above, we do plan to more carefully examine the longitudinal causal effects of supervision in our members looking at both load progression, and also the isometric strength test data we routinely collect which we believe may better tease out this as a possible explanation for the *in situ* results observed.

### Reviewer Comment

Given the limitations presented by the authors, the results provided by the retrospective analysis, and the effect analyzed during the experimental analysis about the comparison of only one session of supervised versus unsupervised one-week apart, the conclusion that “these results in general support prior work highlighting the importance of supervision during RT” seems overstated. While I agree with the authors onthe potential influence of the Hawthorne effect, a more cautious and nuanced interpretation would better reflect the study’s findings and limitations.

### Author Response

Given that we are cautious in our interpretation of the previous observational data results alone, but that the experimental study provides us with causal estimates due to the randomisation and cross-over design, we do not feel that our results are overstated. The experimental findings do support the effects of supervision, but the contrast with the seeming lack of difference in TUL, and the smaller absolute RPEs, in *in situ* data suggests that this effect is difficult to causally identify against the background of potential confounders in observational data. Again, this is why in our next planned staged of this programme of work we are engaging with more appropriate causal designs such as the interrupted time-series with control design [@lopezbernalUseControlsInterrupted2018].

### Reviewer Comment

No conflict of interest is reported, yet the study analyzes the effect of the Kieser Method, a supervised high-intensity training model developed by the Kieser Training Company, with which two of the authors are affiliated. Given this connection, could there be a potential bias in the interpretation or preference for certain results? While this does not undermine the value of the study, acknowledging and addressing this possibility would strengthen the transparency and integrity of the manuscript.

### Author Response

Thank you for noting this. We apologies for not being more explicit. We had mentioned that Kieser had provided in-kind funding for this project and our affiliations as you note are clearly aligned. But we have added a section to be more clear regarding this. We also hope that our transparency in terms of the data, materials, code, and indeed the results (which to some extent suggest that our in clinic protocols are not in fact being adhered to... something we have fed back internally and are looking at how to address and also evaluate prospectively the approaches we take to this) also highlight that we are trying to minimise any affiliational bias as much as possible.

## Reviewer 3 - Anonymous

### Reviewer Comment

I have gone through the study and need the following recommendations for the final decision

### Author Response

Many thanks for your review.

### Reviewer Comment

1. The abstract is well-written and explained, but it would benefit from being divided into distinct sections, such as background, methodology, results, and conclusion.

### Author Response

We have not made this change for now as the journals we may potentially submit to upon recommendation (either Communications in Kinesiology or PeerJ) do not typically require this format. If a journal subsequently requires this we will make the change in line with their requirements.

### Reviewer Comment

2. There is only one line about RT. A few more lines at the start of the abstract would be beneficial for the reader.

### Author Response

The abstract is already quite lengthy and hence we have kept this general information to a minimum opting to get straight to summarising the study itself. The introduction provides more exposition on the broader topic.

### Reviewer Comment

3. The authors used the word "little" in "exercise performance differed little between supervised and unsupervised training." It would be better to use some technical words because it shows subjectivity rather objectivity. What is meant by little can be explained numerically.

### Author Response

It is hard to avoid using imprecise descriptors of the magnitude of difference and impossible to avoid making some subjective determination of whether a result is big enough or small enough to care or not care about relative to typical values of the outcome and other background information. Though, the manuscript and abstract provide the precise numerical estimates for the values we are admittedly subjectively interpreting here and so any reader can interpret these themselves deciding if they agree with the difference being "little".

### Reviewer Comment

4.The introduction is well written and it contains latest studies. but it should be extended more.

### Author Response

Without suggestion of what could be included to extend it we have not added anything further. The manuscript is already quite long and we believe we have provided the background as succinctly as possible in the introduction already and do not require any further detail.

### Reviewer Comment

5.The software used for the study should also be mentioned.

### Author Response

Any specific software used for protocols such as the mobile phone app is already mentioned, and we link out to an extensive list generated using the `grateful` package already containing all of the software used for analysis including version numbers - https://osf.io/ew79g. This is also included in the `renv` lockfile such that anyone reproducing our analyses can utilise the exact versions we had utilised.

### Reviewer Comment

6.The result section should be explained for the general readers to understand the technical outcomes. It would be better to make statements simple while explaining technical words.

### Author Response

As suggested by reviewer 1 we have added a lay explanation of the models, and have also added a visual to help with interpretation of the models and results.

### Reviewer Comment

7.The authors mentioned about the confidence intervals and quantile intervals. Are there any more measures to show the strength of outcomes like effect size ?

### Author Response

This is a common misonception in the field; namely that by *effect size* something like a standardised effect size e.g., Cohen's d is meant. All of the point estimates and the corresponding interval estimates are in fact effect size estimates in and of them selves and in the units of interest to a reader i.e., seconds, probability of stopping, percentage effort/discomfort. So the strength of the outcomes can be interpreted from these directly.

### Reviewer Comment

8.Overall, the study is new and well articulated and would provide reader a quality study.

### Authors Response

Thank you for the kinds words.

### Reviewer Comment

9.Actual real life contribution of this study should be highlighted in the conclusion section. What it can bring in real life?

### Authors Response

We would prefer to leave out inclusion of "real life contribution" such as practical recommendations from this work. In fact, the typical inclusion of practical recommendations by many applied journals in our field from a single study always feels unwarranted and results in overstretching of conclusions. Neither of the journals we are considering to submit to require practical recommendations of this kind. We would note in response though that a very real outcome from this work has for us at Kieser Australia to internally consider how we might adapt our operational procedures to try and ensure that our protocols as prescribed are in fact being followed by members and trainers. Our future work will look to evaluate this more closely as we implement changes.

# References
